Self Regulation Ontology Retest Analyses

### 2018-06-05 code/SRO_Retest_Analyses.Rmd
adding post frisem analyses

  out = data.frame(r2_lit = summary(mod_lit)$r.squared,
                   r2_boot = summary(mod_boot)$r.squared,
                   m_lit = coef(summary(mod_lit))["lit_predictor","Estimate"],
                   m_boot = coef(summary(mod_boot))["mean_pearson","Estimate"])

@@

Are you at noise ceiling for suveys vs. tasks?

@@

Is this because of less data on surveys? Should I be using a different metric for goodness of fit?

```{r}
table(rel_comp$task)
```

@@

Our data is better in predicting the literature for the surveys that it is in predicting tasks.

@@

@@

@@

@@

Are you better in estimating the literature using our data for surveys vs tasks?

@@

>>>>

  out = data.frame(r2_lit = summary(mod_lit)$adj.r.squared,
                   r2_boot = summary(mod_boot)$adj.r.squared,
                   m_lit = coef(summary(mod_lit))["lit_predictor","Estimate"],
                   m_boot = coef(summary(mod_boot))["mean_pearson","Estimate"])

@@

Are you at noise ceiling for suveys vs. tasks? Are you better in estimating the literature using our data for surveys vs tasks?

@@

@@

Our data is better in predicting the literature estimates for the surveys that it is in predicting tasks.

@@

### LOOCV predicting lit vs our data

@@

```{r}
pred_sample <- function(df){

  get_sample_row <- function(df){
    if(nrow(df)>1){
      row_num = sample(1:nrow(df),1)
      sample_row = df[row_num,]
    }
    else{
      sample_row = df
    }
    return(sample_row)
  }

  test_df = df %>%
    group_by(dv) %>%
    do(get_sample_row(.))

  train_df = anti_join(df, test_df)

  if(length(unique(train_df$task))>1){
    mod = lm(retest_reliability ~ scale(sample_size)+task, data=train_df)
  }
  else{
    mod = lm(retest_reliability ~ scale(sample_size), data=train_df)
  }

  test_df$pred = predict(mod, test_df)

  # out = data.frame(res_lit = sum(test_df$retest_reliability - pred)^2,
  #                  res_boot = sum(test_df$mean_pearson - pred)^2)

  return(test_df)
}
```

```{r message=FALSE}
pred_sample_out = plyr::rdply(1000, pred_sample(rel_comp))
```

Plot difference between

pred_sample_out %>%
  select(pred, retest_reliability, mean_pearson) %>%
  gather(key, value, -pred) %>%
  mutate(diff = pred - value) %>%
  ggplot(aes(value, fill=key))+
  geom_density(position = "identity", color=NA, alpha=0.5)+
  scale_fill_manual(breaks=c("mean_pearson","retest_reliability"),
                       labels=c("Empirical", "Literature"),
                      name="Predicting",
                      values = c("purple", "orange"))

Plot difference between prediction and value broken down by measure type

```{r}
pred_sample_out %>%
  select(task, pred, retest_reliability, mean_pearson) %>%
  gather(key, value, -task, -pred) %>%
  mutate(diff = pred - value) %>%
  ggplot(aes(value, fill=key, color=task, alpha=task))+
  geom_density(position = "identity", size=2)+
  scale_fill_manual(breaks=c("mean_pearson","retest_reliability"),
                       labels=c("Empirical", "Literature"),
                      name="Predicting",
                      values = c("purple", "orange"))+
  scale_alpha_manual(breaks=c("survey", "task"),
                     values = c(0.4, 0.7),
                     name="Measure type")+
  scale_color_discrete(name="Measure type")
```

Data versus model prediction plot

@@

Distributions of sum squared residual

### Measure level comparison

@@

@@

### Meaningful variables

ADD!!!!
